---
title: "NCAP Summaries"
author: "Last Updated"
date: '`r format(Sys.time(), "%B %d, %Y %r %Z")`'
output:
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes
    toc_depth: 5
  word_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width = 3, fig.asp = 0.618, out.width = "100%", fig.align = "center", dev='svg')
```

```{r}
library(openxlsx)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DiagrammeR)
library(ggthemes)
library(scales)
library(DiagrammeRsvg)
library(svglite)
library(rsvg)
library(png)
library(XML)
library(data.table)
library(table1)
library(pander)
library(kableExtra)
library(ggconsort)

panderOptions('table.split.table', Inf)
```

```{r, eval=FALSE}
# https://github.com/tgerke/ggconsort
# https://tgerke.github.io/ggconsort/

https://youtu.be/a8A638n6Qew 

devtools::install_github("tgerke/ggconsort")
```

```{r}
tkns <- read.xlsx("tokens.xlsx")

library(REDCapR)
uri <- "https://redcap2.nyu.edu/api/"
token <- tkns[1,2]

meta_DT <- redcap_metadata_read(redcap_uri = uri, token=token)$data

names(meta_DT)[1:6] <- c("var","form","header","type","label","choices")

setDT(meta_DT)

meta_DT[grepl("^round|^sum", choices) == TRUE, choices := NA]
meta_DT[type %in% c("calc","slider","dropdown"), choices := NA]
meta_DT[var == "loc_language", choices := NA]

meta_DT[!is.na(choices), choices := paste(gsub(";", ",", choices))]
meta_DT[!is.na(choices), choices := paste(gsub("Don't", "Do not", choices))]
meta_DT[!is.na(choices), choices := paste(gsub("0, No\\|1, Yes\\|997, Do not Know", "0, No \\| 1, Yes \\| 997, Do not Know", choices))]
meta_DT[!is.na(choices), choices := paste(gsub("0, No\\| 1, Yes", "0, No \\| 1, Yes", choices))]
meta_DT[!is.na(choices), choices := paste(gsub("1, Not at all \\| 2, A little\\|3, Somewhat \\|4, Quite a bit \\|5, A great deal  \\|997, Do not Know \\| 998, Refuse to Answer",
                                               "1, Not at all \\| 2, A little \\| 3, Somewhat \\| 4, Quite a bit \\| 5, A great deal \\| 997, Do not Know \\| 998, Refuse to Answer", choices))]
meta_DT[!is.na(choices), factlab := paste(gsub(" \\| ", "';", gsub("([0-9]), ", "\\1='", gsub("'", "", choices))), "'", sep = "")]
meta_DT[!is.na(label), attriblab := gsub("\n", "", label)]
meta_DT[!is.na(attriblab), attriblab := gsub("<[^>]*>", "", attriblab)]

meta_DT[!is.na(choices), factlab := gsub("<.*?>", "", factlab)]
meta_DT[!is.na(attriblab), attriblab := gsub("<.*?>", "", attriblab)]

DT <- REDCapR::redcap_read_oneshot(redcap_uri=uri, raw_or_label = "raw", token=token)$data
DT_n <- REDCapR::redcap_read_oneshot(redcap_uri=uri, raw_or_label = "raw", token=token)$data

# setDT(DT)

## Recode Multiple Choice Fields to Factors
val_labs <- intersect(meta_DT$var[!is.na(meta_DT$choices)], names(DT))

vlabmatch <- data.frame(var = val_labs, 
                        DT_index = match(val_labs, names(DT)),
                        ddict_index = match(val_labs, meta_DT$var))

vlabmatch$factlab <- meta_DT$factlab[vlabmatch$ddict_index]

for(i in 1:length(val_labs)){
DT[,vlabmatch$DT_index[i]] <- car::recode(var = DT[,vlabmatch$DT_index[i]], 
                                                recodes = vlabmatch$factlab[i],
                                                levels = strsplit(x = gsub("\\d+=|'", "", vlabmatch$factlab[i]), split = ";")[[1]],
                                                as.factor = TRUE)
}

## Apply Variables Labels
var_labs <- intersect(meta_DT$var[!is.na(meta_DT$attriblab)], names(DT))

alabmatch <- data.frame(var = var_labs,
                        DT_index = match(var_labs, names(DT)),
                        ddict_index = match(var_labs, meta_DT$var))

# alabmatch$fieldlabel <- paste(alabmatch$var, meta_DT$attriblab[alabmatch$ddict_index], sep = ": ")

alabmatch$fieldlabel <- meta_DT$attriblab[alabmatch$ddict_index]

for(i in 1:length(var_labs)){
attributes(DT[, alabmatch$DT_index[i]])$label <- alabmatch$fieldlabel[i]  
}

setDT(DT)
setDT(DT_n)
```

```{r}
DT[participant_id == "DMA010287F", participant_id := "DOMA010287"]
DT[participant_id == "SBO070186M", participant_id := "SHBO070186"]
```

```{r, eval = FALSE}
save(list=c('DT'), file = "ncap.Rdata")
```

```{r}
ncap_cohort <- DT %>% 
  cohort_start("Screening Consent Initiated<br>") %>%
    cohort_define(
    scr1 = .full %>% filter(redcap_event_name == "screener_consent_arm_1" & screening_consent_form_complete %in% c(0,1,2)),
    scr2 = .full %>% filter(redcap_event_name == "screener_arm_1"),
    s2_e = .full %>% filter(redcap_event_name == "screener_arm_1" & eligibility == 'ELIGIBLE'),
    s2_ie = .full %>% filter(redcap_event_name == "screener_arm_1" & eligibility == 'INELIGIBLE'),
    enrl = .full %>% filter(redcap_event_name == "consent_form_arm_2" & consent_form_complete == 2),
    bl = .full %>% filter(redcap_event_name == "baseline_interview_arm_2" & !is.na(n_baseline_end)),
    rand = .full %>% filter(redcap_event_name == "randomization_arm_2" & !is.na(rand_condition))
    ) %>%
  cohort_label(
    scr1 = "Screening Consent<br>Initiated<br>",
    scr2 = "Full Screening<br>Initiated<br>",
    s2_e = "Eligible<br>",
    s2_ie = "Ineligible<br>",
    enrl = "Enrolled<br>",
    bl = "Baseline Interview<br>",
    rand = "Assigned to Condition<br>"
  )
```

```{r}
study_consort <- ncap_cohort %>%
  consort_box_add(
    "scr1", 0, 50, cohort_count_adorn(ncap_cohort, scr1)
  ) %>%
  consort_box_add(
    "scr2", 0, 40, cohort_count_adorn(ncap_cohort, scr2)
  ) %>%
    consort_box_add(
    "s2_ie", 10, 37.5, cohort_count_adorn(ncap_cohort, s2_ie)
  ) %>%    
      consort_box_add(
    "s2_e", 0, 30, cohort_count_adorn(ncap_cohort, s2_e)
  ) %>%    
      consort_box_add(
    "bl", 0, 20, cohort_count_adorn(ncap_cohort, bl)
  ) %>%    
      consort_box_add(
    "rand", 0, 10, cohort_count_adorn(ncap_cohort, rand)
  ) %>%    
 consort_arrow_add(start = "scr1", end = "scr2", end_side = "top") %>%
# consort_arrow_add(start = "scr2", end = "s2_ie", start_side = "right", end_side = "left") %>%
  consort_arrow_add(start_x = 0, start_y = 37.5, end = "s2_ie", end_side = "left") %>%
  consort_arrow_add(start = "scr2", end = "s2_e", end_side = "top") %>%
     consort_arrow_add(start = "s2_e", end = "bl", end_side = "top") %>%
  consort_arrow_add(start = "bl", end = "rand", end_side = "top") 
```

# CONSORT
```{r, include = TRUE, fig.width = 9, fig.height = 4, dev='svg'}
study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 4, margin_v = 4)
```

# Enrollment
```{r, fig.asp=1, out.width = "60%"}
enroll_new <- data.frame(day = seq(as.Date("2022-07-01"), as.Date("2023-08-01"), 1))

setDT(enroll_new)

DT[, bl_date := as.Date(format(n_baseline_end, "%Y-%m-%d"))]

enroll_new <- merge(enroll_new, DT[!is.na(bl_date), .(Enrolled = .N), by = .(bl_date)], by.x = "day", by.y = "bl_date", all=TRUE)

enroll_new[is.na(Enrolled), Enrolled := 0]
enroll_new[, Row := 1:.N]
enroll_new[, Target := 0.6801008]
enroll_new[, `Cumulative Enrolled` := cumsum(Enrolled)]
enroll_new[, `Cumulative Target` := cumsum(Target)]
enroll_new[, Deficit := `Cumulative Target` - `Cumulative Enrolled`]

enroll_new_m <- melt(enroll_new, id.vars = c("day","Row"), 
                     variable.name = "type",
                     value.name = "num")

figtop <- ceiling(enroll_new_m[day == Sys.Date() & type %in% c('Cumulative Enrolled','Cumulative Target'), .(max(num))])$V1

while(figtop %% 8 > 0) {figtop <- figtop + 1}

ggplot(enroll_new_m[day <= Sys.Date() & type %in% c('Cumulative Enrolled','Cumulative Target'),], 
       aes(x = day, y = num, group = type, color = type)) + 
  geom_path() +
  scale_y_continuous(limits=c(0,figtop), breaks=seq(0,figtop,8)) +
  scale_x_date(date_breaks = "1 week", date_labels = "%b-%d") +
  ylab("Cumulative Number Enrolled") + xlab("") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        axis.title.y = element_text(size=6),
        legend.position="bottom", 
        legend.text=element_text(size=6),
        legend.title = element_blank())
```

```{r}
enroll_new[day == Sys.Date(), .(`Cumulative Enrolled`, 
                                `Cumulative Target` = ceiling(`Cumulative Target`), 
                                `Current Deficit` = ceiling(Deficit))] %>%
  kbl(., booktabs = T, escape = F, align = "c") %>%
  kable_paper("hover", full_width = FALSE)
```

# Select Screening Items
```{r}
DT[, screening_complete := car::recode(screening_complete, "0='Incomplete';1='Unverified';2='Complete'", as.factor = TRUE)]
label(DT$screening_complete) <- "Screening Complete?"

table1(~ consent_given + n_recruitment_method + 
         n_interview_format + age_yrs + 
         bio_sex_birth_2 + 
         current_county + tested_for_covid + tested_positive_for_covid +
         screening_complete + eligibility, 
       data = DT[redcap_event_name == "screener_arm_1",])
```

## Vaccination (among those eligible on earlier criteria)
```{r}
label(DT$covid_vaccine) <- "Have you received a COVID-19 vaccine?(RADxUP CDE #90)"

table1(~ covid_vaccine, 
       data = DT[scr_notif_14 == "No (Participant meets ALL eligibility criteria so far - ask MVR questions)" &
                 redcap_event_name == "screener_arm_1",])
```

### Willing to check records (among those eligible on earlier criteria and with a Yes or No response to vaccination)
```{r}
table1(~ n_mvr, 
       data = DT[covid_vaccine %in% c('Yes','No') &
                 scr_notif_14 == "No (Participant meets ALL eligibility criteria so far - ask MVR questions)" &
                 redcap_event_name == "screener_arm_1",])
```

### Proof method among those reporting vaccination and eligible on earlier criteria
```{r}
table1(~ n_vaccine_proof, 
       data = DT[covid_vaccine %in% c('Yes') &
                 scr_notif_14 == "No (Participant meets ALL eligibility criteria so far - ask MVR questions)" &   
                 redcap_event_name == "screener_arm_1",])
```

### Vaccine received among those reporting vaccination and eligible on earlier criteria
```{r}
DT[, vaccine_dose := car::recode(vaccine_dose, "1='One';2='Two';3:hi='Three or More'", 
                                 as.factor = TRUE, levels = c('One','Two','Three or More'))]

label(DT$vaccine_manufac_2) <- "Who was the manufacturer of the most recent vaccine you received? (RADxUP CDE #181)"
label(DT$vaccine_dose) <- "How many doses have you received?(RADxUP CDE #183)"

table1(~ vaccine_manufac_2 + vaccine_dose, 
       data = DT[covid_vaccine %in% c('Yes') &
                 scr_notif_14 == "No (Participant meets ALL eligibility criteria so far - ask MVR questions)" &   
                 redcap_event_name == "screener_arm_1",])
```

### What does documentary evidence show among those providing it
```{r}
DT[, n_dose_check := car::recode(n_dose_check, "0='No';1='Yes'", as.factor = TRUE)]

label(DT$n_dose_check) <- "Does vaccination card or documentary evidence indicate that participant has 2 or more doses of any COVID-19 vaccine?"

table1(~ n_dose_check, 
       data = DT[scr_notif_14 == "No (Participant meets ALL eligibility criteria so far - ask MVR questions)" &
                 !is.na(n_vaccine_proof) &
                 n_vaccine_proof %in% c('My Vaccine Record', 
                                        'CDC Vaccination Card', 
                                        'Other documentary evidence') &
                 redcap_event_name == "screener_arm_1",])
```

# Reasons for Ineligibility
```{r}
DT[redcap_event_name == "screener_arm_1", 
     `:=` (IE_consent = consent_given == "No, consent is not required/is waived for this study",
           IE_age = age_yrs < 18 | age_yrs > 70,
           IE_race_ethn = (race_ethn_hispanic == "No, not of Hispanic, Latino, or Spanish origin" | race_ethn_hispanic == "Prefer not to answer") & 
                          (race_ethn_race___1 == 1 |
                           race_ethn_race___3 == 1 | 
                           race_ethn_race___4 == 1 |
                           race_ethn_race___5 == 1 |
                           race_ethn_race___15 == 1) &
                           race_ethn_race___1 != 1,
           IE_language = n_language != "Yes",
           IE_location = n_current_location == "No",
           IE_work = n_work_status == "No",
           IE_occupation = n_current_occupation == "Other" | n_current_occupation == "Prefer not to answer",
           IE_vaccine = (covid_vaccine == "Yes" & vaccine_manufac_2 == "Johnson & Johnson") | vaccine_dose != "One",
           IE_covid_test = n_tested_for_covid_6mo != "No",
           IE_previous = n_previous_participation == "Yes",
           IE_cab = n_cab_member == "Yes",
           IE_guidelines = n_covid_guidelines == "No",
           IE_cell = n_cell_use == "No",
           IE_symptoms = n_covid_symptoms_2wks == "Yes")]

label(DT$IE_consent) <- "No consent given"
label(DT$IE_age) <- "Does not meet age criteria"
label(DT$IE_race_ethn) <- "Does not identify as part of an eligible racial/ethnic group"
label(DT$IE_language) <- "Cannot participate in activities conducted in English or Spanish"
label(DT$IE_location) <- "Does not live in NYC"
label(DT$IE_work) <- "Has not worked full-time or part-time in the past month"
label(DT$IE_occupation) <- "Does not work in an eligble occupation"
label(DT$IE_vaccine) <- "Fully vaccinated"
label(DT$IE_covid_test) <- "Tested for COVID in the past six months"
label(DT$IE_previous) <- "Previous participant"
label(DT$IE_cab) <- "CAB Member"
label(DT$IE_guidelines) <- "Not willing to follow NYU COVID guidelines"
label(DT$IE_cell) <- "No cell phone for study participation"
label(DT$IE_symptoms) <- "COVID Symptoms in Past Two Weeks"
```

```{r}
table1(~ ., data = DT[redcap_event_name == "screener_arm_1", .SD, .SDcols = names(DT) %like% "^IE_"])
```
# Select Baseline Items
```{r}
table1(~ edu_years_of_school + gender_identity_term + sex_orient_id +
         selfphysical_parent + selfmental_parent +
         household_famgen_3 + household_homeless + 
         discrimination_ethnicity, 
       data = DT[redcap_event_name == "baseline_interview_arm_2",])
```

# Time Spent on Core (Minutes)
```{r}
label(DT$np_core_timespent) <- "Enter amount of time spent on Core activities"

table1(~ np_core_timespent, 
       data = DT[grepl("^core", redcap_event_name),])
```

```{r, eval=FALSE}
DT_id <- data.frame(pid = unique(DT$participant_id))
setDT(DT_id)

DT_id[, Screeening_Consent := pid %in% DT$participant_id[DT$redcap_event_name == "screener_consent_arm_1"]]
DT_id[, Screeening_Main := pid %in% DT$participant_id[DT$redcap_event_name == "screener_arm_1"]]
DT_id[, Enroll_Consent := pid %in% DT$participant_id[DT$redcap_event_name == "consent_form_arm_2"]]
DT_id[, Baseline := pid %in% DT$participant_id[DT$redcap_event_name == "baseline_interview_arm_2"]]
DT_id[, Randomized := pid %in% DT$participant_id[DT$redcap_event_name == "randomization_arm_2"]]
```



